---
title: "Crab Research Proj"
output:
  html_document:
    df_print: paged
---

### Team:
- Alina Muliak
- Olexiy Hoiev
- Oleksandra Stasiuk


```{r}
library(ggplot2)
```

```{r}
data <- read.csv("./CrabAgePrediction.csv", TRUE)

data <- data[,-6:-8]
data <- data[order(data$Age),]
data$Length[1:100]
plot(data, col="purple")
plot(data$Height, col="purple")
```

```{r}
ggplot(data) +
    geom_density(aes(x = Length, fill = Sex), alpha = 0.5) +
    labs(y = "Density", x = "Length", fill = "Nitrogen\nConcentration") +
    scale_fill_manual(labels = c("M", "F", "I"),
        values = c("#DB24BC", "#BCDB24", "#24BCDB")) +
    theme_minimal()
ggplot(data) +
    geom_density(aes(x = Age, fill = Sex), alpha = 0.6) +
    labs(y = "Density", x = "Age", fill = "Nitrogen\nConcentration") +
    scale_fill_manual(labels = c("M", "F", "I"),
        values = c("#DB24BC", "#BCDB24", "#24BCDB")) +
    theme_minimal()
head(data)
```

```{r}
mydata <- read.csv("./CrabAgePrediction.csv", TRUE)
summary(mydata)
```
**ANOVA** is an extension of a $t$-test. With a $t$-test you can test 2 groups.....тут треба описати що це таке ANOVA

$F$-value:
$$F = \frac{\text{Between group variatioin}}{\text{Within group variation}}$$
If most of the variation comes from within groups, then 'some component' probably does not have much of any effect, however, if the variation seems most to come from between the groups, this would indicate that 'some component' does probably have an effect.

Thus, larger $F$-ratios indicate there's a high probability that the groups do have different means; in other words, it does make a difference.
High $f$-ratio combined with a small $p$-value means that 'some component' most likely does have an effect and we should reject the null hypothesis that the means are the same.


```{r}
fit <- aov(Age ~ Weight + Diameter + Sex + Length + Height, data=mydata)
summary(fit)
```
